\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright{}
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}
    % \usepackage{hyperref}
    \usepackage[hidelinks, colorlinks=false]{hyperref}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill\\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder{}
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep{0pt} \itemsep{-2pt}}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge {Sahaj Singh}}\\
    \vspace{1mm}
	British Columbia $\cdot$ \href{mailto:sahaj_singh@sfu.ca}{sahaj\_singh@sfu.ca} $\cdot$ \href{http://sahajs.com}{sahajs.com}\\
\end{center}

%==== Skills ====%
\header{Skills}
\begin{tabular}{ l l }
	\textbf{Programming Languages:} & C, C++, Python, MATLAB, Java, Assembly, HTML5/CSS3, Javascript \\
	\textbf{Tools \& Technologies:} & Git VC, Visual Studio Code, PyCharm, macOS, Linux, Windows         \\
\end{tabular}
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{MathWorks} \hfill Burnaby, BC\\
\text{MATLAB --- SFU Student Ambassador} \hfill Oct 2022 --- Present\\
\vspace{-3mm}
\begin{itemize} \itemsep-3pt
	\item Organizing and hosting numerous programming and simulation based events revolving around MATLAB and Simulink.
	\item Helping in the process of creating meaningful relationships between MATLAB and professors/students at SFU.\@ Providing support for students with questions related to MATLAB and Simulink.
\end{itemize}
\vspace{-1mm}
\textbf{picoTera Electronics Inc.} \hfill Richmond, BC\\
\text{Software/Firmware Developer} \hfill Jan 2022 --- April 2022\\
\vspace{-3mm}
\begin{itemize} \itemsep-3pt
	\item Developed advanced firmware features in C for communication devices operating on PSoC6 embedded platforms. Designed and implemented custom feature sets to enhance device functionality and user experience.
	\item Constructed tailored datasets to facilitate the training and optimization of Recurrent Neural Network (RNN) models for effective noise reduction in smart denoising applications.
	\item Integrated Bluetooth Low Energy (BLE) between the PSoC6 device (firmware written in C) and an Android application (written in Java), enabling real-time, efficient data transmission and bolstering overall user experience.
\end{itemize}

%==== Projects ====%
\header{Projects}
\vspace{1mm}

\href{https://github.com/SatireSage/Multi-threaded-Memory-Allocator}{\textbf{Multi-threaded Memory Allocator}} {\sl C, Make\/}
\vspace{-2mm}
\begin{itemize} \itemsep-3pt
    \item Developed a multi-threaded memory allocator in C, supporting First Fit, Best Fit, and Worst Fit allocation algorithms.
    \item Implemented features such as allocator initialization, allocation/deallocation interfaces, metadata management, compaction support, statistics reporting, multi-threading support, and uninitialization.
    \item Designed test cases and provided usage instructions to ensure the proper functionality and efficiency.
\end{itemize}

\href{https://github.com/SatireSage/FPGA-UART-Protocol}{\textbf{FPGA UART Protocol Implementation}} {\sl VHDL, Modelsim, Altera DE2\/}
\vspace{-2mm}
\begin{itemize} \itemsep-3pt
    \item Developed a UART protocol for the Altera DE2 FPGA, featuring baud rate generation, data framing, error detection and correction, and handshaking subsystems.
    \item Implemented in VHDL with comprehensive testbenches to verify the functionality of both the transmitter and receiver modules.
    \item Enabled synchronous data transmission between UART devices and allowed for seamless operation via onboard switches and keys for data input, baud rate selection, and module reset.
\end{itemize}

\href{https://github.com/SatireSage/Dronee}{\textbf{Drone Controller and System}} {\sl Embedded C, Arduino (C++), Beaglebone\/}
\vspace{-2mm}
\begin{itemize} \itemsep-3pt
    \item Designed a wireless drone system using a BeagleBone Green and Arduino Nano 33 IOT drone.
    \item Developed multiple control modes, integrated LCD display, and implemented an ultrasonic sensor for gesture-based height control.
    \item Wrote a custom driver for efficient BLE communication between the controller and drone.
    \item Incorporated a watchdog and systemd script for automated restarts to handle any unexpected system crashes.
\end{itemize}

\href{https://github.com/SatireSage/FASTrack}{\textbf{FASTrack - Reaction Time Game}} {\sl Assembly, Embedded C, Zedboard\/}
\vspace{-2mm}
\begin{itemize} \itemsep-3pt
    \item Developed a reaction time-based game called FASTrack for the Xilinx ZedBoard, utilizing the ARM7 assembly instruction set.
    \item Implemented various game features such as multiple speed modes and user controls through switches. Utilized OLED display and LEDs for visual feedback.
    \item Demonstrated key concepts including timer interrupts, masking, OLED display usage, and Finite State Machines (FSMs).
\end{itemize}

%==== Education ====%
\header{Education}
\textbf{B.A.Sc. Computer Engineering - Honours}\hfill Burnaby, BC\\
Simon Fraser University \hfill Sep 2020 --- Sep 2025\\
\vspace{1mm}

%==== Awards ====%
\header{Awards}
\textbf{Innovation Award}/\textbf{ESSS Award: 2022} \hfill SFU --- Engineering Science Student Society\\
Honors contributions to the student society and Recognized for outstanding creativity, originality, and impact via my projects driving advancements in technology.\\
\vspace*{1mm}

\end{document}