\documentclass[letterpaper,11pt]{article}
    \usepackage{times}
    \usepackage{latexsym}
    \usepackage[empty]{fullpage}
    \usepackage{titlesec}
    \usepackage{marvosym}
    \usepackage[usenames,dvipsnames]{xcolor}
    \usepackage{verbatim}
    \usepackage{enumitem}
    \usepackage[hidelinks, colorlinks=false]{hyperref}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{fancyhdr}
    \usepackage[english]{babel}
    \usepackage{tabularx}
    \usepackage{fontawesome5}
    \input{glyphtounicode}
    
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%----Resume Definitions----%

\definecolor{colorValue}{RGB}{72, 114, 103}

% Sections formatting:
\titleformat{\section}{
    \vspace{-13pt}\scshape\raggedright\large\color{colorValue}\bfseries
}{}{0em}{}[\color{black}\titlerule{}\vspace{-5pt}]

% Custom commands:
\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill\\
}

\newcommand{\contact} [5] {
    \begin{center}
        \textbf{\color{colorValue}\Huge #1} \\ \vspace{1pt}
        \small {\faIcon{map-marker-alt}} \underline{#5} $|$ {\faIcon{phone} \underline{#2}} $|$ \href{mailto:#3}{\faIcon{envelope} \underline{#3}} $|$ 
        \href{#4}{\faIcon{linkedin} \underline{Rose--Epstein}} 
    \end{center}
}

\newcommand{\Item} [1] {
    \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\employer} [5] {
    {\textbf{#3} \hfill \textbf{#4 --- #5}\\ \textbf{\emph{#1}} \hfill #2\\}
}

\newcommand{\school} [6] {
    {\textbf{#1} --- #3 \hfill \textbf{#2}\\ #4 -- \emph{#6} \hfill #5\\}
}


\newcommand{\workItemListStart} [0] {
    \vspace{-1pt}
    \begin{itemize}[topsep=0pt,itemsep=-2pt]
}

\newcommand{\workItemListEnd} [0] {
    \end{itemize}
    \vspace{1pt}
}

\newcommand{\resumeItemListStart} [0] {
    \vspace{2pt}
    \begin{itemize}[topsep=0pt,itemsep=-2pt]
}

\newcommand{\resumeItemListEnd} [0] {
    \end{itemize}
    \vspace{5pt}
}
%----End of Resume Definitions----%

\begin{document}
    \vspace*{-30pt}

    %----Profile----%
    % chktex-file 8
    % chktex-file 12
    % chktex-file 29
    \contact{Rose Epstein}{+1(306) 850 7153}{rea13@sfu.ca}{https://www.linkedin.com/in/rose-epstein/}{Vancouver, BC}
    %----End of Profile----%

    %----Education----%
    \section{EDUCATION}
    \school{Simon Fraser University}{Graduation: Dec 2025}{BASc. in Engineering Science}{Computer Engineering}{Burnaby, BC}{CGPA: 3.14}
    \school{University of Saskatchewan}{Sept 2016 --- June 2020}{BSc. in Biomedical Sciences}{Physiology \& Pharmacology}{Saskatoon, SK}{Graduated with Great Distinction}
    %----End of Education----%
    
    %----Skills----%
    \section{TECHNICAL SKILLS}
    \begin{itemize}[leftmargin=0in, label={}]
        \small{\item{
            \textbf{Programming Languages:}{ C / C++, VHDL, SQL, MATLAB, Haskell} \\
            \textbf{Tools, Frameworks \& Technologies:}{ Git, Visual Studio Code, Quartus Prime, Xilinx Vivado and Vitis, Linux, macOS, Windows} \\
            \textbf{Relevant Courses:}{ Embedded Systems, Digital Systems Design, Advanced Digital Systems, Programming for Heterogeneous Systems} \\
        }}
        \end{itemize}
    %----End of Skills----%

    %----Experience----%
    \section{WORK EXPERIENCE}
    \employer{Epic Semiconductors}{Vancouver, BC}{Application Engineer}{Jan}{Apr 2022}
    \workItemListStart{}
        \Item{Executed experiments for process and product development, including circuit analysis, populating PCBs with SMD soldering, and performing debugging and verification.}
        \Item{Managed an ECG-signal producing PCB project for client demonstrations, including breadboard testing and circuit analysis, 
                programming for signal generation, PCB design and population, and extensive testing to achieve successful results.}
        \Item{Designed and tested a gesture detection circuit for future client demonstrations, performing initial circuit analysis and extensively testing on a breadboard to optimize design prior to implementation.}
        \workItemListEnd{}
    %----End of Experience----%

    %----Awards----%
    \section{LEADERSHIP EXPERIENCE}
    \employer{Women in Engineering (WiE)}{Burnaby, BC}{Co-President}{May 2022}{2023}
    \workItemListStart{}
        \Item{Led and coordinated a team to manage various social, academic, internal, and external responsibilities.}
        \Item{Facilitated club meetings with club members, encouraging effective communication and supporting a strong sense of teamwork and community.}
        \Item{Built relationships with SFU faculty, other SFU clubs, and external organizations to organize events, create networking opportunities, and secure funding and resources for female students at SFU and in the broader community.}
    \workItemListEnd{}
    %----End of Awards----%

    %----Projects----%
    \section{PROJECT EXPERIENCE}
    {{\color{colorValue}} \underline{\textbf{Interrupt Driven Graphical Interface on FPGA:}}} \hfill \textbf{Spring 2024}
    \resumeItemListStart{}
        \Item{Designed an interrupt-driven VGA graphical interface on Xilinx Zedboard, with push button input for real-time user interaction.}
        \Item{Developed an interrupt service routine in C++ to handle real-time GPIO events to ensure proper graphical display for VGA output.}
        \Item{Thoroughly tested and integrated graphical elements, verifying visual accuracy and smooth screen updates in response to GPIO inputs.}
    \resumeItemListEnd{}
    {{\color{colorValue}} \underline{\textbf{Graphical 2D Game Application on FPGA with Vivado and Vitis:}}} \hfill \textbf{Spring 2024}
    \resumeItemListStart{}
    \Item{Developed a 2D Graphical Snake Game on Xilinx Zedboard utilizing Vivado and Vitis tools, optimizing memory usage and performance.}
    %\Item{Designed game logic in software using C++ and created all custom graphics with GiMP, including game screens, sprites and animations.}
    \Item{Implemented seamless gameplay mechanics and menu navigation all with smooth real-time screen display updates.}
    \Item{Integrated the interrupt-driven graphical VGA interface with the SoC, creating a seamless embedded system.}
    \Item{Independently designed, implemented, and tested the hardware using Xilinx Vivado, the software using Xilinx Vitis.}
    \resumeItemListEnd{}
    %{{\color{colorValue}} \underline{\textbf{Gaussian Elimination Kernel FPGA Optimization with C++:}}} \hfill \textbf{Fall 2023}
    %\resumeItemListStart{}
    %    \Item{Implement an FPGA acceleration project on the Gaussian Elimination kernel from GPU benchmark suite Rodinia using High-Level Synthesis (HLS) C++.}
    %    \Item{Optimized the data transfer between the host and FPGA with memory coalescing optimizations}
    %\resumeItemListEnd{}
    {{\color{colorValue}} \underline{\textbf{Customized UART Protocol on FPGA with VHDL:}}} \hfill \textbf{Summer 2023}
    \resumeItemListStart{}
        \Item{Implemented UART protocol on Altera DE2 FPGA using VHDL, with baud rate generation, data framing, and error detection.}
        \Item{Collaborated with a team to design, implement, and optimize a UART protocol in VHDL.}
        \Item{Developed the transmitter component to send data serially to the receiver, taking input data from the on-board switches, with transmission initiated by a key press.}
        \Item{Extensively tested the transmitter and receiver components, both individually and in conjunction with the SoC, using testbenches in ModelSim.}
    \resumeItemListEnd{}
    %{{\color{colorValue}} \underline{\textbf{Roulette Game on FPGA with VHDL:}}} \hfill \textbf{Summer 2023}
    %\resumeItemListStart{}
    %    \Item{Implemented UART protocol on the Altera DE2 FPGA using VHDL, with baud rate generation, data framing and error detection.}
    %    \Item{Coordinated with a group to design, implement, and optimize a UART protocol in VHDL on the FPGA board.}
    %    \Item{Implemented the transmitter component to send data serially to the receiver, and extensively tested the entire system with a testbench using ModelSim.}
    %\resumeItemListEnd{}
    %{{\color{colorValue}} \underline{\textbf{Scrolling Message Display on FPGA with VHDL}}} \hfill \textbf{Fall 2021}
    %\resumeItemListStart{}
    %    \Item{Developed a VHDL program for the Altera DE2-115 board, to display a scrolling message on HEX display.}
    %    \Item{Coordinated with a group of two to develop a custom instruction set for ASIP to meet the program requirements}
    %    \Item{Implemented user interface for user input through the on board push-button to trigger different displays.}
    %\resumeItemListEnd{}
    %----End of Projects----%

\end{document}