\documentclass[letterpaper,11pt]{article}
    \usepackage{times}
    \usepackage{latexsym}
    \usepackage[empty]{fullpage}
    \usepackage{titlesec}
    \usepackage{marvosym}
    \usepackage[usenames,dvipsnames]{xcolor}
    \usepackage{verbatim}
    \usepackage{enumitem}
    \usepackage[hidelinks, colorlinks=false]{hyperref}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{fancyhdr}
    \usepackage[english]{babel}
    \usepackage{tabularx}
    \usepackage{fontawesome5}
    \input{glyphtounicode}
    \usepackage{lipsum}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom{}
\setlength{\tabcolsep}{0in}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%----Resume Definitions----%

\definecolor{colorValue}{RGB}{72, 114, 103}

% Sections formatting:
\titleformat{\section}{
    \vspace{-13pt}\scshape\raggedright\large\color{colorValue}\bfseries
}{}{0em}{}[\color{black}\titlerule{}\vspace{-5pt}]

% Custom commands:
\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill\\
}

\newcommand{\contact} [4] {
    \begin{center}
        \textbf{\color{colorValue}\Huge #1} \\ \vspace{1pt}
        \small {\faIcon{phone} \underline{#2}} $|$ \href{mailto:#3}{\faIcon{envelope} \underline{#3}} $|$ 
        \href{#4}{\faIcon{linkedin} \underline{Rose--Epstein}} $|$
    \end{center}
}

\newcommand{\roleName}{Embedded Software Developer}
\newcommand{\company}{Zaber Technologies\hspace{4px}}

\begin{document}
    \vspace*{-30pt}

    %----Profile----%
    % chktex-file 8
    % chktex-file 12
    % chktex-file 29
    \contact{Rose Epstein}{+1(306)-850-7153}{rea13@sfu.ca}{https://www.linkedin.com/in/rose-epstein/}
    %----End of Profile----%

    \section{Cover Letter}
    \setlength{\parindent}{0pt}
    \vspace*{10pt}

    \par \textbf{Adam Hurrell}
    \par Unit 2 - 605 W Kent Avenue North
    \par North Vancouver, BC, V6P 6T7
    \vspace*{10pt}
    \par \textbf{\color{colorValue} RE: \roleName{}} Role

    \vspace*{10pt}
    \par Dear Hiring Manager,  \hfill \textbf{\today}
    \vspace*{10pt}
    \par I am delighted to be applying for the \roleName{} role at \company{}
    \vspace*{10pt}
    \par I am a fourth-year Computer Engineering student in the Engineering Science program at Simon Fraser University. I successfully
    completed a Bachelor of Science degree majoring in Physiology and Pharmacology at the University of Saskatchewan in Saskatoon in the Summer 0f 2020.
    Throughout my academics and past employment in professional work settings, I have developed excellent verbal and written communication skills. 
    During my years at SFU, I have been involved with the Women in Engineering (WiE) club. Through this, I have created many meeting templates and led numerous event planning discussions. 
    WiE is a part of many events at SFU, but being a speaker for the annual Ecole Polytechnique Massacre Memorial is one of the most memorable for me. 
    Not only was I a part of a powerful conversation regarding gender-based violence, but I was also able to showcase my new found confidence in public speaking. 
    \vspace*{10pt}
    \par Moreover, during my studies, I have developed a foundational understanding of digital logic design, VHDL, and C/C++ programming languages. 
    One of my accomplished projects from this year is a graphical application on the Xilinx Zedboard, our rendition of the classic Snake Game. This project reinforced 
    my ability to communicate and make decisions effectively with a partner. The most interesting part of developing this project was implementing a 
    custom interrupt-driven VGA IP block for real-time graphics and its integration with the rest of the system.
    \vspace*{10pt}
    \par I would like to thank you for giving me the opportunity to express my interest in working alongside
    the talented \company team. I believe my past experience, both academically and professionally, makes
    me a unique fit for this position. I am available for 8 months. If you have any questions, feel free to contact me via email. I hope to hear from you
    soon. Thank you again for your consideration.
    \vspace*{10pt}
    \par Sincerely,
    \par Rose Epstein
\end{document}
