\documentclass[letterpaper,11pt]{article}
    \usepackage{times}
    \usepackage{latexsym}
    \usepackage[empty]{fullpage}
    \usepackage{titlesec}
    \usepackage{marvosym}
    \usepackage[usenames,dvipsnames]{xcolor}
    \usepackage{verbatim}
    \usepackage{enumitem}
    \usepackage[hidelinks, colorlinks=false]{hyperref}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{fancyhdr}
    \usepackage[english]{babel}
    \usepackage{tabularx}
    \usepackage{fontawesome5}
    \input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%----Resume Definitions----%

\definecolor{colorValue}{RGB}{27, 71, 127}

% Sections formatting:
\titleformat{\section}{
    \vspace{-13pt}\scshape\raggedright\large\color{colorValue}\bfseries
}{}{0em}{}[\color{black}\titlerule{}\vspace{-5pt}]

% Custom commands:
\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill\\
}

\newcommand{\contact} [5] {
    \begin{center}
        \textbf{\color{colorValue}\Huge #1} \\ \vspace{1pt}
        \small \href{https://#2}{\faIcon{code} \underline{#2}} $|$ \href{mailto:#3}{\faIcon{envelope} \underline{#3}} $|$ 
        \href{#4}{\faIcon{linkedin} \underline{Sahaj--Singh}} $|$
        \href{#5}{\faIcon{github} \underline{SatireSage}}
    \end{center}
}

\newcommand{\Item} [1] {
    \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\employer} [5] {
    {\textbf{#3} \hfill \textbf{#4 --- #5}\\ \textbf{\emph{#1}} \hfill #2\\}
}

\newcommand{\school} [6] {
    {\textbf{#1} \hfill \textbf{#5 --- #6}\\ \textbf{#3} \hfill #2\\ \begin{itemize}[topsep=0pt,itemsep=-2pt]\item{\textbf{\emph{#4}}}\end{itemize}}
}

\newcommand{\workItemListStart} [0] {
    \vspace{-1pt}
    \begin{itemize}[topsep=0pt,itemsep=-2pt]
}

\newcommand{\workItemListEnd} [0] {
    \end{itemize}
    \vspace{1pt}
}

\newcommand{\resumeItemListStart} [0] {
    \vspace{2pt}
    \begin{itemize}[topsep=0pt,itemsep=-2pt]
}

\newcommand{\resumeItemListEnd} [0] {
    \end{itemize}
    \vspace{5pt}
}
%----End of Resume Definitions----%

\begin{document}
    \vspace*{-30pt}

    %----Profile----%
    % chktex-file 8
    % chktex-file 12
    % chktex-file 29
    \contact{Sahaj Singh}{sahajs.com}{sahaj\_singh@sfu.ca}{https://www.linkedin.com/in/sahaj--singh/}{https://github.com/SatireSage}
    %----End of Profile----%

    %----Skills----%
    \section{TECHNICAL SKILLS}
    \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
        \textbf{Programming Languages:}{ C / C++, VHDL, Python, MATLAB, Bash, Java, Assembly, HTML5/CSS3, Javascript, Flutter} \\
        \textbf{Tools, Frameworks \& Technologies:}{ Linux, Git, Jira, React, TensorFlow, PyCharm, Visual Studio Code, macOS, Windows, Android} \\
        \textbf{Linux:}{ Admin, Bash, Kernel Config, Package Mgmt (APT, YUM), Networking, UFW/iptables, FS Mgmt, cron, SSH} \\
        \textbf{Relevant Courses:}{ Embedded Systems, Digital Systems Design, Fundamentals of Digital Logic and Design} \\
    }}
    \end{itemize}
    %----End of Skills----%

    %----Experience----%
    \section{WORK EXPERIENCE}
    \employer{Microchip Technology Inc.}{Burnaby, BC}{CBU Software Engineer}{Jan 2024}{Present}
    \workItemListStart{}
        \Item{Reviewing the datasheet for the \textbf{Meta DX2+} and \textbf{META-DX} chipset.}
        \Item{Developing/supporting test framework for both pre-silicon and post-silicon testing.}
        \Item{Setup and configuration evaluations boards for \textbf{SW verification}.}
    \workItemListEnd{}
    \employer{Simon Fraser University}{Burnaby, BC}{ENSC 252 | Fundamentals Of Digital Logic & Design | Teaching Assistant (TA)}{Sep 2023}{Dec 2023}
    \workItemListStart{}
    \Item{Assist students in understanding \textbf{digital logic and design concepts} during lab sessions, tutorials, and office hours.}
    \Item{Designed, supervised, and graded \textbf{bonus projects} to test students' understanding of the course material. Incorporated Concepts such as \textbf{One Hot Encoding, Debouncing Circuits,} and \textbf{Finite State Machines {Moore}}.}
    \Item{Verified pre-existing lab solutions, documented any issues that arose and added additional components to the lab material.}
    \workItemListEnd{}
    \employer{picoTera Electronics Inc.}{Richmond, BC}{Software/Firmware Developer}{Jan}{April 2022}
    \workItemListStart{}
        \Item{Developed advanced firmware using \textbf{Object-Oriented Programming (OOP)} principles in \textbf{C/C++} for \textbf{PSoC6 and ARM Cortex-M4, M0 platforms} and ported the project from PSoC creator to ModusToolbox 2.4 for better compatibility.}
        \Item{Implemented modifications to a \textbf{TensorFlow based Recurrent Neural Network (RNN) model written in Python} and \textbf{ported in C} for Cortex-M4 devices, reducing noise in audio denoising applications approximately from \textbf{90+ decibels down to 60 decibels.} Additionally, created a custom audio dataset to train the RNN model, increasing the variety of noise profiles for training by a factor of 3.}
        % \Item{Replaced dynamic gain with static gain, optimizing post-processing audio quality, and \textbf{boosting denoising performance by 25\%.}}
        \Item{Authored custom \textbf{cmake scripts for CMSIS libraries}, reducing memory usage and storage in complex operations and enabled Bluetooth Low Energy \textbf{(BLE) integration} between PSoC6 and an Android app, facilitating real-time data transmission.}
    \workItemListEnd{}
    %----End of Experience----%

    %----Projects----%
    \section{PROJECT EXPERIENCE}
    \href{https://github.com/SatireSage/FPGA-UART-Protocol}{{\color{colorValue}\faIcon{link}} \underline{\textbf{FPGA-UART-Protocol:}}} \hfill \textbf{Spring 2023}
    \resumeItemListStart{}
        \Item{Implemented the \textbf{UART protocol for the Altera DE2 FPGA}, featuring baud rate generation, data framing, error detection and correction, and handshaking subsystems.}
        \Item{Designed a full-fledged VHDL implementation, bolstered by \textbf{comprehensive testbenches and simulations} to ensure proper functionality across both transmitter and receiver modules.}
        \Item{Enabled \textbf{synchronous data transmission between UART devices} and allowed for seamless operation via onboard switches and keys for data input, baud rate selection, and module reset.}
    \resumeItemListEnd{}
    % \href{https://github.com/SatireSage/FASTrack}{{\color{colorValue}\faIcon{link}} \underline{\textbf{FASTrack - Reaction Time Game:}}} \hfill \textbf{Summer 2022}
    % \resumeItemListStart{}
    %     \Item{Developed a reaction time-based game for the Xilinx ZedBoard, utilizing the \textbf{ARM7 assembly instruction} set.}
    %     \Item{Implemented various game features such as multiple speed modes and user controls through switches. Utilized OLED display and LEDs for visual feedback.}
    %     \Item{Demonstrated key concepts including timer interrupts, masking, OLED display usage, and \textbf{Finite State Machines (FSMs)}.}
    % \resumeItemListEnd{}
    \href{https://github.com/SatireSage/Scrolling-Message-Display-Board}{{\color{colorValue}\faIcon{link}} \underline{\textbf{Scrolling Message Display Board (SMDB):}}} \hfill \textbf{Fall 2021}
    \resumeItemListStart{}
        \Item{Developed VHDL code to drive scrolling messages on a HEX display, ensuring fluid motion and clear visibility.}
        \Item{Designed a \textbf{custom Instruction Set Architecture for the ASIP} to meet the board's specific demands.}
        \Item{Deployed and rigorously tested the entire system via testbenches and on an \textbf{Altera DE2-115 board using Quartus} via c\textbf{ustom/edge cases}, confirming stable performance and reliability.}
    \resumeItemListEnd{}
    %----End of Projects----%

    %----Education----%
    \section{EDUCATION}
    \school{Simon Fraser University}{Burnaby, BC}{B.A.Sc. Computer Engineering}{Computing Science Minor}{Sep 2020}{Present}
    %----End of Education----%

    %----Awards----%
    \section{LEADERSHIP EXPERIENCE}
    \employer{MathWorks}{Burnaby/Surrey, BC}{MATLAB --- SFU Student Ambassador}{Oct 2022}{Present}
    \workItemListStart{}
        \Item{Organizing and hosting numerous programming and simulation based events revolving around \textbf{MATLAB and Simulink.}}
        \Item{Providing support for students with MATLAB and Simulink.\@ Creating meaningful relationships between \textbf{MathWorks and SFU.}}
    \workItemListEnd{}
    %----End of Awards----%

\end{document}